Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
Add the top-level algorithm.

However, more details are needed when doing the implementation. 
In our prototype we start directly with open pNets expressed
programmatically, using the pNet API (graphical editors may be added
later). 
%From these, we compute
%the open automaton of an open pNet. We explain here our main
%implementation choices.
%:
%\begin{itemize}
%  \item Steps 2a-2b are merged, applying Tr2 from the
%premisses OTs from subnets to generate OTs without
%explicitely constructing the deduction tree.
%  \item We define a general naming schema for implementing the fresh 
%and clone functions with more structure than a simple global name
%generator. It ensures unicity, but builds names
%readable enough for debugging purpose.
%  \item Besides that, we also have designed a management of state variables and
%    assignments throughout the whole computation.
%%%   \item Satisfiability check is done only at
%%% top level of the open-transition construction. An alternative would be
%%% to submit the satisfiability check to the SMT solver at each level of
%%% the hierarchical OT construction, potentially reducing the overall number of
%%% combinations. But the submission to the SMT engine is costly, and more
%%% complexity analysis is required before deciding if this would be
%%% worthwhile. 
%\end{itemize}
%
%In the following sections, we detail:
%\begin{itemize}
%\item The structure of fresh variable names.
%\item The details of the implementation for step 2a-2b, refined into:
%  \subitem combining all possibilities of subnets activity/inactivity,
%  \subitem matching each combination with synchronization vectors.
%\item Management of local variables of pLTSs.
%\item Pruning unsatisfiable OTs using the Z3 SMT solver.
%\end{itemize}

@@

\paragraph{Combining:}
Algorithm 1 shows the combining algorithm for enumerating all possible
working status combinations from subnets. Dealing with a list $TR$
containing  sets of open transitions from different subnets,
the algorithm choses one of sets $L_{ot}$ and does combining on the
remaining part of $TR$ recursively. The case when a subnet is not working is
managed by adding a $null$ into the $L_{ot}$.

@@

\paragraph{Matching:} Algorithm 2 shows the algorithm matches
combination $L_C$, hole behaviors $B$ with synchronization vectors
$SV$ according to the definition of the predicate declared before. We
clone the $sv$ using the fresh function to generate a new $sv'$ with
fresh variables.The mismatch on working status is easy to detect so we
filter them in the algorithm through checking the matching elements
$e_1$ and $e_2$. 
Then we build the resulting open transition. Satisfiability of the
predicate is not checked at this level, but only later, at the
toplevel of the pNet.

>>>>

However, more details are needed when doing the implementation. 
Algorithm 1 shows there are much more things added, such as how we apply 
the Tr1 or Tr2.

\begin{algorithm}
\caption{Open Automaton Generation}
\begin{algorithmic}[1]

\State Initialize a set for unexplored global states $U$, a set for explored global states $E$;
\State Initialize the initial global state $G$ of the open automaton, add it into $U$;
\State Initialize a list $L$ for storing open transitions;
\While{!isEmpty(U)}
	\State Extract a global state $S$ from the $U$;
	\State For the pNet node, recursively applying Tr1 or Tr2 on its subnets;
	\If{Subnet is pLTS, apply the Tr1} 
		\State Generate open transition $OT$ according to the transitions in pLTS;
	\EndIf
	\If{Subnet is pNet, apply the Tr2} 
		\For{each $sv \in SV$}
			\State Invoke $Combining()$ to generate the combination of sub-transitions;
			\State Invoke $Matching()$ to match the combination with the $sv$;
			\State Generate open transition $OT$ using the predicate from the former steps;
		\EndFor
	\EndIf
	\State Store $OT$ into $L$;
	\State Get the target global state $T$ from $OT$;
	\If{$(U.contains(T))\ ||\ (E.contains(T))$} 
		\State Add $T$ into the $U$;
	\EndIf
\EndWhile
\State Prune the open transitions in $L$ using SMT solver;
\State \Return $L$;

In our prototype we start directly with open pNets expressed
programmatically, using the pNet API (graphical editors may be added
later). 
%From these, we compute
%the open automaton of an open pNet. We explain here our main
%implementation choices.
%:
%\begin{itemize}
%  \item Steps 2a-2b are merged, applying Tr2 from the
%premisses OTs from subnets to generate OTs without
%explicitely constructing the deduction tree.
%  \item We define a general naming schema for implementing the fresh 
%and clone functions with more structure than a simple global name
%generator. It ensures unicity, but builds names
%readable enough for debugging purpose.
%  \item Besides that, we also have designed a management of state variables and
%    assignments throughout the whole computation.
%%%   \item Satisfiability check is done only at
%%% top level of the open-transition construction. An alternative would be
%%% to submit the satisfiability check to the SMT solver at each level of
%%% the hierarchical OT construction, potentially reducing the overall number of
%%% combinations. But the submission to the SMT engine is costly, and more
%%% complexity analysis is required before deciding if this would be
%%% worthwhile. 
%\end{itemize}
%
%In the following sections, we detail:
%\begin{itemize}
%\item The structure of fresh variable names.
%\item The details of the implementation for step 2a-2b, refined into:
%  \subitem combining all possibilities of subnets activity/inactivity,
%  \subitem matching each combination with synchronization vectors.
%\item Management of local variables of pLTSs.
%\item Pruning unsatisfiable OTs using the Z3 SMT solver.
%\end{itemize}

@@

\paragraph{Combining:}
Algorithm 2 shows the combining algorithm for enumerating all possible
working status combinations from subnets. Dealing with a list $TR$
containing  sets of open transitions from different subnets,
the algorithm choses one of sets $L_{ot}$ and does combining on the
remaining part of $TR$ recursively. The case when a subnet is not working is
managed by adding a $null$ into the $L_{ot}$.

@@

\paragraph{Matching:} Algorithm 3 shows the algorithm matches
combination $L_C$, hole behaviors $B$ with synchronization vectors
$SV$ according to the definition of the predicate declared before. We
clone the $sv$ using the fresh function to generate a new $sv'$ with
fresh variables.The mismatch on working status is easy to detect so we
filter them in the algorithm through checking the matching elements
$e_1$ and $e_2$. 
Then we build the resulting open transition. Satisfiability of the
predicate is not checked at this level, but only later, at the
toplevel of the pNet.
